### 2023-01-13 _posts/papers-2023.tex
Add ispc citation

>>>>

\section*{Compilers}
\begin{itemize}
    \item The paper presents ispc --- Intel SPMD Program Compiler. The paper introduces new SPMD-on-SIMD concept that seems to be quite reasonable for running effectively compiling SPMD programs for CPUs. A few specific optimizations are introduced to enable efficient usage of a CPU's SIMD hardware unit. The project looks like an interesting alternative to hand-written intrinsic-based optimizations. The project is still alive at the moment of writing the note. I can also see a few well familiar names in the list of contributors. As a side note, the paper can be a good reference for \href{https://github.com/yulyugin/mipt-parallel-computing}{<<MIPT parallel computing>> course>>} if that one ever gets back to live:

    \cite{Pharr:ispc:2012}.
\end{itemize}
